---
title: "publishing_cran"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{publishing_cran}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(project.aid)
```

## Releasing to CRAN-checklist

Consider avoiding `ren` when publishing to CRAN. THis has caused so much trouble, and really is only necessary on collaborative data projects to streamline the analyses.

THe checklist below really is the same no matter if you are updating or publishing first version.

- [ ] Commit all changes to GIT

- [ ] Update docs and check package locally

```{r eval=FALSE}
devtools::check(
  document = TRUE,
  manual = TRUE,
  remote = TRUE,
  incoming = TRUE
)
```

Copy results to `cran-comments.md`

- [ ] Checks for publishing with RHUB

```{r eval=FALSE}
# If not already setup, then initialise RHUB with the two following lines and follow instructions in the console.
# rhub::rhub_setup()
# rhub::rhub_doctor() # THis is also the command for trouble shooting

rhub::rhub_check(platforms = c(
  "linux",
  "macos",
  "macos-arm64",
  "windows"))
```

Let it run. Takes less than an hour. Check results in GitHub.

- [ ] Release on CRAN (make sure to answer all questions prompted)

```{r eval=FALSE}
devtools::release()
```

Follow instruction on e-mail to confirm upload

- [ ] When approved, release to GitHub (this also publishes newest version to Zenodo if setup)

```{r eval=FALSE}
usethis::use_github_release()
```
